Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/paper.tex
small fixes

In practical cases, non-linearities and sampling error will add noise to the diagonal elements of $\hat H$. We need to test whether diagonal elements are different from zero. The average value $\mu$ of non-zero coefficients of $\text{diag}(\hat H)$ is the trace of $\hat H$ divided by $k$. $\mu$ can be estimated as follow :
\begin{equation}
$\mu = \frac{Var(X)}{Var(X)+Var(N)}$
\end{equation}
This provides a method to identify causal features
%Since $X$ and $N$ are not correlated, $\Sigma_{X_1 X_1}^{-1}\Sigma_{N_1 N_1}$ should have a low condition number, which means  should provide a good estimate of $\frac{1}{k}Tr(\hat H)$.

@@

We perform two experiments to evaluate B2B: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography (MEG) dataset.
%
We use scikit-learn's PLS and RidgeCV \citep{sklearn} as well as pyrcca' regularized canonical compnent analysis (RegCCA, \citep{bilenko2016pyrcca}) objects to compare B2B against the standard baselines.

>>>>

In practical cases, non-linearities and sampling error will add noise to the diagonal elements of $\hat H$. We need to test whether diagonal elements are different from zero. The average value $\mu$ of non-zero coefficients of $\text{diag}(\hat H)$ is the trace of $\hat H$ divided by $k$. $\mu$ can be estimated as follow :
\begin{equation}
\mu = \frac{Var(X)}{Var(X)+Var(N)}
\end{equation}
This provides a method to identify causal features
%Since $X$ and $N$ are not correlated, $\Sigma_{X_1 X_1}^{-1}\Sigma_{N_1 N_1}$ should have a low condition number, which means  should provide a good estimate of $\frac{1}{k}Tr(\hat H)$.

@@

We perform two experiments to evaluate B2B: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography (MEG) dataset.
%
We use scikit-learn's PLS and RidgeCV \citep{sklearn} as well as pyrcca's regularized canonical component analysis (RegCCA, \citep{bilenko2016pyrcca}) objects to compare B2B against the standard baselines.
